Gamification Effectiveness on Education

### 2024-04-18 paper/paper.qmd
finished the second dicussion point

Like I mentioned before gamification has to potential to change the traditional educational system, but in order to do that need to design it in a way that truly benefits the students. A leading expert in gamification and behavioral drive, Yu-kai Chou, has a create framework for gamification called the Octalysis Framework(reference to the figure in the appendix).Looking at the framework there are eight main points mention: Epic Meaning, Accomplishment, Empowerment, Ownership, Social Influence, Scarcity, Unpredictability, and Avoidance.

@@

Another example that we want to apply this framework is on a popular gamification language learning app, called Duolingo.

## Student's feedback

>>>>

Like I mentioned before gamification has to potential to change the traditional educational system, but in order to do that need to design it in a way that truly benefits the students. A leading expert in gamification and behavioral drive, Yu-kai Chou, has a create framework for gamification called the Octalysis Framework(reference to the figure in the appendix).Looking at the framework there are eight main points mention: Epic Meaning, Accomplishment, Empowerment, Ownership, Social Influence, Scarcity, Unpredictability, and Avoidance. For even more in depth explanation, please visit Yu-kai website:https://yukaichou.com/gamification-examples/octalysis-complete-gamification-framework/.

@@

Another example that we want to apply this framework is on a popular gamification language learning app, called Duolingo. Duolingo is a free app that has miliions of user ranging from public students in third world countries to even hollywood stars. Yu-kai Chou website provides an analysis for Duolingo, which has 6 out of 8 elements of the framework and here I am going to highlight some of the elements. Firstly, Epic Meaning is to learn a language and the app even asks the user when creating an account what is their purpose for learning new language. Secondly, Ownership, users have a currency call Lingots which allows players to buy Power-Ups(ways to make the player stronger) such as streak freeze and to buy clothes for their player character. Lastly, it has Scarcity and Avoidance as player have a limited amount of lives and if they lose then they can no longer play for a certain of time. 
## Student's feedback
